\large{Vipassana for Hackers} \\ \Huge{The Proposal} \\ \large\textit{Version 0.1}

### 2019-11-30 the-proposal/the-proposal.tex
proposal: add hildt ref

Third is the exploratory research intended to objectively define
consciousness. As such research must pertain to all forms of consciousness it
therefore includes all non-human forms of consciousness. Findings will inform our
understanding of the Mind-Body Problem of psychology and philosophy, the entire field
of bioethics, and --- perhaps most importantly --- the nascent field of Artificial
Consciousness as a subfield of Artificial Intelligence. As of this writing, this
overarching integral field of study has yet to emerge and has no name as a discipline.

@@

>>>>

Third is the exploratory research intended to objectively define
consciousness. As such research must pertain to all forms of consciousness it
therefore includes all non-human forms of consciousness. Findings will inform our
understanding of the Mind-Body Problem of psychology and philosophy, the entire field
of bioethics, and --- perhaps most importantly --- the nascent field of Artificial
Consciousness as a subfield of Artificial Intelligence. \cite{hildt2019} As of this
writing, this overarching integral field of study has yet to emerge and has no name
as a discipline.

@@

\bibitem{hildt2019}
  Artificial Intelligence: Does Consciousness Matter?
  \todo{stop doing this and use bibtex}
